---
title: "Developing Countries with Net-Zero Target"
author: "CDMMP"
output: 
  html_document:
      toc: true
      toc_float: true
  
---
```{r setup, include=FALSE}
version <- "04042024_v6"
N <- 104
J <- 34

# Loading libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(R.matlab)
library(readxl)
library(cowplot)
library(patchwork)
library(ggthemes)
library(ggrepel)

# Setting working directories
PROJECT <- dirname(dirname(getwd()))
DATA <- file.path(PROJECT, "data")
OUTPUT <- file.path(PROJECT, "output")
knitr::opts_chunk$set(dev="png")
```

```{r, echo = F}

Outliers_Part2 <- function(plot){
  
  plot_build <- ggplot_build(plot)
  
  # Extract outlier data
  outlier_country <- c()
  outlier_name <- c()
  outlier_group <- c()
  outlier <- plot_build$data[[1]]$outliers
  for (i in c(1:length(outlier))){
    outlier_country[[i]] <- 
      national_emissions_hat[national_emissions_hat$value %in% outlier[[i]],"code"]
    outlier_name[[i]] <-
      national_emissions_hat[national_emissions_hat$value %in% outlier[[i]],"name"]
    outlier_group[[i]] <-
      national_emissions_hat[national_emissions_hat$value %in% outlier[[i]],"group"]
  }
  
  outlier_annotations<-
  data.frame(value = unlist(outlier),
             country = unlist(outlier_country),
             name = unlist(outlier_name),
             group = unlist(outlier_group))
  
  plot + 
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) 

}


Outliers <- function(data, plot){
  
  plot_build <- ggplot_build(plot)
  
  # Extract outlier data
  outlier_country <- c()
  outlier_name <- c()
  outlier_group <- c()
  outlier_trade_flow <- c()
  outlier_coalition <- c()
  outlier <- plot_build$data[[1]]$outliers
  for (i in c(1:length(outlier))){
    outlier_country[[i]] <- 
      data[data$value %in% outlier[[i]],"code"]
    outlier_name[[i]] <-
      data[data$value %in% outlier[[i]],"name"]
    outlier_group[[i]] <-
      data[data$value %in% outlier[[i]],"group"]
    outlier_trade_flow[[i]] <-
      data[data$value %in% outlier[[i]],"trade_flow"]
    outlier_coalition[[i]] <-
      data[data$value %in% outlier[[i]],"coalition"]
  }
  
  if (length(outlier_trade_flow) == 0){
    outlier_trade_flow <- outlier_group

  }
  if (length(outlier_coalition) == 0){
    outlier_coalition <- outlier_group
  }
  
  outlier_annotations<-
  data.frame(value = unlist(outlier),
             country = unlist(outlier_country),
             name = unlist(outlier_name),
             group = unlist(outlier_group),
             trade_flow = unlist(outlier_trade_flow),
             coalition = unlist(outlier_coalition))
  
  return(outlier_annotations)
  
  
}
```


# Summary 
This script synthesizes the results for different domestic and trade carbon policies in 48 developing countries with net-zero emissions targets.

These results assume a social cost of carbon equal to \$190 and a carbon price equal to [\${carbon}](carbon_price_selection.html) (click here to view the results at different carbon prices).

The countries we study are listed below. Each link will take you to an in-depth, country level analysis. 

```{r, echo=F, results='asis'}
countries <- read_excel(file.path(DATA, 
                                  paste0("dictionary_GTAP_", version, ".xlsx")), 
                        sheet = "Developing")
countries <- rbind(data.frame(id = 0, code = "ALL", country="All"), countries)
for(c in c(1:nrow(countries))) {
  cat("- ", paste0("[",countries$country[c], "](", countries$code[c], "_{carbon}.html)"),
      "\n")
}
```


Our counterfactuals are split into two parts.

**Part 1**

CTF1: Setting tariffs to bilateral mean (Shapiro)

CTF2: Setting tariffs to OECD mean

CTF3: Carbon policy

CTF4: Carbon policy + CBAM

**Part 2** 

CTF5: Large country coalition

CTF6: Large country coalition + developing country respond with equivalence

CTF7: Large country coalition + developing country respond without equivalence

```{r, include=FALSE, warning=F}
# Loading ID data
countries <- read_excel(file.path(DATA, 
                                  paste0("dictionary_GTAP_", version, ".xlsx")), 
                        sheet = "Developing")
sectors <- read_excel(file.path(DATA, 
                                paste0("dictionary_GTAP_",version,".xlsx")), 
                      sheet = "labels_sec")
LAC <- read_excel(file.path(DATA, 
                            paste0("dictionary_GTAP_", version, ".xlsx")), 
                  sheet = "LAC")
Eurasia <- read_excel(file.path(DATA, 
                            paste0("dictionary_GTAP_", version, ".xlsx")), 
                  sheet = "Eurasia")
Africa <- read_excel(file.path(DATA, 
                            paste0("dictionary_GTAP_", version, ".xlsx")), 
                  sheet = "Africa")
Regions <- rbind(LAC, Eurasia, Africa)

colnames(sectors) <- c("id", "code", "sector")


CTF1 <-
  c("Bilateral mean",
    "OECD mean",
    "Carbon policy (EITE + CO2)",
    "Carbon policy + CBAM (EITE + CO2)",
    "Carbon policy (ALL + GHG)",
    "Carbon policy + CBAM (ALL + GHG)")
CTF2 <-
    c("No Response",
    "Response w/ equivalence",
    "Response w/o equivalence")
CTF1 <- factor(CTF1, levels = CTF1)
CTF2 <- factor(CTF2, levels = CTF2)
# EITE Sectors
EITE  <- c(15,16,17,20,21,22,28)
```

# Part 1

```{r, echo = F, warning=F}
# Now loading in the full sample results for counterfactuals 6 and 7, both of which loop through each country in our sample.
WELFARE <- c()
EXPORTS <- c()
IMPORTS <- c()
EMISSIONS <- c()

CTF_part1 <-
  list.files(file.path(
    OUTPUT,
    "quantitative",
    substr(version, nchar(version) - 1, nchar(version)),
    "full_sample_part1"
  ))
contains_carbon_price <- sapply(CTF_part1, function(x) grepl("{carbon}", x))
CTF_part1 <- CTF_part1[contains_carbon_price]
CTF_part1 <- CTF_part1[c(1,2,4,6,3,5)]
for (ctf in c(1:length(CTF_part1))) {
# for (ctf in c(3,4,5)) {
  data <- readMat(file.path(
    OUTPUT,
    "quantitative",
    substr(version, nchar(version) - 1, nchar(version)),
    "full_sample_part1",
    CTF_part1[ctf]
  ))
  
  WELFARE <- rbind(WELFARE,
                   data.frame(
                     name = CTF1[ctf],
                     value = (data$WELFARE - 1) * 100,
                     country = countries$id
                   ))
  EXPORTS <- rbind(EXPORTS,
                   data.frame(
                     name = CTF1[ctf],
                     value = (data$EXPORTS - 1) * 100,
                     country = countries$id
                   ))
  
  IMPORTS <- rbind(IMPORTS,
                   data.frame(
                     name = CTF1[ctf],
                     value = (data$IMPORTS - 1) * 100,
                     country = countries$id
                   ))
  EMISSIONS <- rbind(EMISSIONS,
                     data.frame(
                       name = CTF1[ctf],
                       value = (data$EMISSIONS - 1) * 100,
                       country = countries$id
                     ))
  
}

EXPORTS$trade_flow <- "Export"
IMPORTS$trade_flow <- "Import"
TRADE_FLOWS <- rbind(EXPORTS, IMPORTS)


WELFARE <-
  merge(WELFARE,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
EXPORTS <-
  merge(EXPORTS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
IMPORTS <-
  merge(IMPORTS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
TRADE_FLOWS <-
  merge(TRADE_FLOWS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
EMISSIONS <-
  merge(EMISSIONS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)

```

## Welfare

```{r, echo=F, fig.width=12, warning=F}
WELFARE_PLOT <-
  ggplot(WELFARE, aes(x = name, y = value)) +
  geom_boxplot(outlier.shape = 1,
               width = .25,
               fill = "gray") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Welfare change (%)",
       title = "% Change in welfare by counterfactual") +
  theme(axis.text.x = element_text(angle = 25, vjust = .5)) +
  theme_hc()
outlier_annotations <- Outliers(WELFARE, WELFARE_PLOT)

(
  WELFARE_PLOT <-
    WELFARE_PLOT +
    geom_text_repel(
      data = outlier_annotations,
      aes(x = name, y = value, label = country),
      box.padding = 0.35,
      point.padding = 0.5,
      min.segment.length = unit(0, 'lines'),
      size = 3
    )
)

```



```{r, echo=F, fig.width=10, fig.height=10, warning=F}
WELFARE_REGION_PLOT <-
  ggplot(WELFARE, aes(
    x = interaction(group, name),
    y = value,
    fill = group
  )) +
  geom_boxplot(outlier.shape = 1, width = .5) +
  facet_wrap(~ name, scales = "free_x", ncol = 2) + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start = .3, end = 1) +
  labs(x = "",
       y = "Welfare change (%)",
       title = "% Change in welfare by counterfactual",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(WELFARE, WELFARE_REGION_PLOT)


(
  WELFARE_REGION_PLOT <-
    WELFARE_REGION_PLOT +
    geom_text_repel(
      data = outlier_annotations,
      aes(
        x = interaction(group,name),
        y = value,
        label = country
      ),
      box.padding = 0.35,
      point.padding = 0.5,
      min.segment.length = unit(0, 'lines'),
      size = 3
    ) + 
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part1)))
)

```

## Trade flows

```{r, echo=FALSE, fig.width=10, fig.height=10, warning=F}
TRADE_FLOWS_PLOT <-
ggplot(TRADE_FLOWS, aes(x = interaction(trade_flow,name), y = value, fill = trade_flow)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, ncol = 2, scale = "free_x") + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "", 
       y = "Multilateral changes in trade (%)", 
       title = "% Change in multilateral trade flows by counterfactual",
       fill = "Trade flows") + 
  theme_hc()


outlier_annotations <- Outliers(TRADE_FLOWS, TRADE_FLOWS_PLOT)

(TRADE_FLOWS_PLOT <-
  TRADE_FLOWS_PLOT + 
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(trade_flow, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3)) + 
  scale_x_discrete(labels = rep(c("Exports", "Imports", length(CTF_part1))))

```

```{r, echo = F, fig.width=10, fig.height=10, warning=F}
EXPORTS_PLOT <-
ggplot(EXPORTS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, ncol = 2, scale = "free_x") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Changes in exports (%)",
       title = "% Change in exports by counterfactual and region",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(EXPORTS, EXPORTS_PLOT)

(EXPORTS_PLOT<-
  EXPORTS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part1))))


IMPORTS_PLOT <-
ggplot(IMPORTS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, ncol = 2, scale = "free_x") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Changes in imports (%)",
       title = "% Change in imports by counterfactual and region",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(IMPORTS, IMPORTS_PLOT)

(IMPORTS_PLOT<-
  IMPORTS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part1))))

```

```{r, echo = F, fig.width=12, warning=F}
EMISSIONS_PLOT <-
ggplot(EMISSIONS, aes(x = name, y = value)) +
  geom_boxplot(fill = "gray", width = 0.5, outlier.shape = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Change in GHG emissions (%)",
       title = "% Change in GHG emissions by counterfactual") +
  theme_hc()

outlier_annotations <- Outliers(EMISSIONS, EMISSIONS_PLOT)

(EMISSIONS_PLOT<-
  EMISSIONS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = name, y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3))
```

## Emissions

```{r, echo = F, fig.width=10, fig.height=10, warning=F}
EMISSIONS_REGIONS_PLOT <-
ggplot(EMISSIONS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, ncol = 2, scale = "free_x") +
  scale_fill_grey(start=.3, end=1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Changes in GHG emissions (%)",
       title = "% Change in GHG emissions by counterfactual and region",
       fill = "Region") +
  theme_hc()

outlier_annotations <- Outliers(EMISSIONS, EMISSIONS_REGIONS_PLOT)

(EMISSIONS_REGIONS_PLOT<-
  EMISSIONS_REGIONS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part1))))


```


# Part 2

```{r, echo=FALSE, fig.width=12, warning=F}
# This first section deals with counterfactual 5. Since it's not looping through each country, we can just load the matrix in one.

CTF_part2 <-
  list.files(file.path(
    OUTPUT,
    "quantitative",
    substr(version, nchar(version) - 1, nchar(version)),
    "full_sample_part2"
  ))
contains_carbon_price <- sapply(CTF_part2, function(x) grepl("{carbon}", x))
CTF_part2 <- CTF_part2[contains_carbon_price]

WELFARE <- c()
EXPORTS <- c()
IMPORTS <- c()
EXPORTS_COALITION <- c()
IMPORTS_COALITION <- c()
EXPORTS_NO_COALITION <- c()
IMPORTS_NO_COALITION <- c()
EMISSIONS <- c()



# data <- readMat(file.path(OUTPUT, "quantitative",
# substr(version, nchar(version)-1, nchar(version)),
# paste0("CTF",toString(ctf),"_{carbon}_", ctf_group, ".mat")))
data <- readMat(file.path(
  OUTPUT,
  "quantitative",
  substr(version, nchar(version) - 1, nchar(version)),
  "full_sample_part2",
  CTF_part2[1]
))


W_hat <- data.frame(name = (data$W.hat.GHG[countries$id] - 1) * 100)
W_hat <- pivot_longer(W_hat, cols = c("name"))
W_hat$name <- CTF2[1]
W_hat$country <- countries$id
WELFARE <- rbind(WELFARE, W_hat)

E_N_hat <- data.frame(name = (data$E.N.hat[countries$id] - 1) * 100)
E_N_hat <- pivot_longer(E_N_hat, cols = c("name"))
E_N_hat$name <- CTF2[1]
E_N_hat$country <- countries$id
EXPORTS <- rbind(EXPORTS, E_N_hat)

M_N_hat <- data.frame(name = (data$M.N.hat[countries$id] - 1) * 100)
M_N_hat <- pivot_longer(M_N_hat, cols = c("name"))
M_N_hat$name <- CTF2[1]
M_N_hat$country <- countries$id
IMPORTS <- rbind(IMPORTS, M_N_hat)

E_N_coalition_hat <- data.frame(name = (data$E.coalition.hat - 1) * 100)
E_N_coalition_hat <- pivot_longer(E_N_coalition_hat, cols = c("name"))
E_N_coalition_hat$name <- CTF2[1]
E_N_coalition_hat$country <- countries$id
EXPORTS_COALITION <- rbind(EXPORTS_COALITION, E_N_coalition_hat)

E_N_no_coalition_hat <- data.frame(name = (data$E.no.coalition.hat - 1) * 100)
E_N_no_coalition_hat <- pivot_longer(E_N_no_coalition_hat, cols = c("name"))
E_N_no_coalition_hat$name <- CTF2[1]
E_N_no_coalition_hat$country <- countries$id
EXPORTS_NO_COALITION <- rbind(EXPORTS_NO_COALITION, E_N_no_coalition_hat)

M_N_coalition_hat <- data.frame(name = (data$M.coalition.hat - 1) * 100)
M_N_coalition_hat <- pivot_longer(M_N_coalition_hat, cols = c("name"))
M_N_coalition_hat$name <- CTF2[1]
M_N_coalition_hat$country <- countries$id
IMPORTS_COALITION <- rbind(IMPORTS_COALITION, M_N_coalition_hat)

M_N_no_coalition_hat <- data.frame(name = (data$M.no.coalition.hat - 1) * 100)
M_N_no_coalition_hat <- pivot_longer(M_N_no_coalition_hat, cols = c("name"))
M_N_no_coalition_hat$name <- CTF2[1]
M_N_no_coalition_hat$country <- countries$id
IMPORTS_NO_COALITION <- rbind(IMPORTS_NO_COALITION, M_N_no_coalition_hat)

national_emissions_hat <-
  data.frame(name = (data$national.emissions.GHG.hat[countries$id] - 1) *
               100)
national_emissions_hat <-
  pivot_longer(national_emissions_hat, cols = c("name"))
national_emissions_hat$name <- CTF2[1]
national_emissions_hat$country <- countries$id
EMISSIONS <- rbind(EMISSIONS, national_emissions_hat)

```

```{r, echo = F, warning=F}
# Now loading in the full sample results for counterfactuals 6 and 7, both of which loop through each country in our sample.

for (ctf in c(2: length(CTF_part2))) {
  data <- readMat(file.path(
    OUTPUT,
    "quantitative",
    substr(version, nchar(version) - 1, nchar(version)),
    "full_sample_part2",
    CTF_part2[ctf]
  ))

  WELFARE <- rbind(WELFARE,
                   data.frame(
                     name = CTF2[ctf],
                     value = (data$WELFARE - 1) * 100,
                     country = countries$id
                   ))
  
  EXPORTS <- rbind(EXPORTS,
                   data.frame(
                     name = CTF2[ctf],
                     value = (data$EXPORTS - 1) * 100,
                     country = countries$id
                   ))
  
  IMPORTS <- rbind(IMPORTS,
                   data.frame(
                     name = CTF2[ctf],
                     value = (data$IMPORTS - 1) * 100,
                     country = countries$id
                   ))
  
  EXPORTS_COALITION <- rbind(EXPORTS_COALITION,
                             data.frame(
                               name = CTF2[ctf],
                               value = (data$E.COALITION-1)*100,
                               country = countries$id
                             ))

  EXPORTS_NO_COALITION <- rbind(EXPORTS_NO_COALITION,
                             data.frame(
                               name = CTF2[ctf], 
                               value = (data$E.NO.COALITION-1)*100,
                               country = countries$id
                             ))

  IMPORTS_COALITION <- rbind(IMPORTS_COALITION,
                             data.frame(
                               name = CTF2[ctf],
                               value = (data$M.COALITION-1)*100,
                               country = countries$id
                             ))

  IMPORTS_NO_COALITION <- rbind(IMPORTS_NO_COALITION,
                             data.frame(
                               name = CTF2[ctf], 
                               value = (data$M.NO.COALITION-1)*100,
                               country = countries$id
                             ))
  
  EMISSIONS <- rbind(EMISSIONS,
                     data.frame(
                       name = CTF2[ctf],
                       value = (data$EMISSIONS - 1) * 100,
                       country = countries$id
                     ))

}

EXPORTS$trade_flow <- "Export"
IMPORTS$trade_flow <- "Import"
TRADE_FLOWS <- rbind(EXPORTS, IMPORTS)

EXPORTS_COALITION$trade_flow <- "Export"
EXPORTS_NO_COALITION$trade_flow <- "Export"

EXPORTS_COALITION$coalition <- "Coalition"
EXPORTS_NO_COALITION$coalition <- "No Coalition"

IMPORTS_COALITION$trade_flow <- "Import"
IMPORTS_NO_COALITION$trade_flow <- "Import"

IMPORTS_COALITION$coalition <- "Coalition"
IMPORTS_NO_COALITION$coalition <- "No Coalition"

TRADE_FLOWS <- rbind(EXPORTS, IMPORTS)
TRADE_FLOWS_COALITION <- rbind(EXPORTS_COALITION, EXPORTS_NO_COALITION,
                               IMPORTS_COALITION, IMPORTS_NO_COALITION)




WELFARE <-
  merge(WELFARE,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
EXPORTS <-
  merge(EXPORTS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
IMPORTS <-
  merge(IMPORTS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
TRADE_FLOWS <-
  merge(TRADE_FLOWS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
TRADE_FLOWS_COALITION <-
  merge(TRADE_FLOWS_COALITION,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T)
EMISSIONS <-
  merge(EMISSIONS,
        Regions,
        by.x = "country",
        by.y = "id",
        all.x = T
  )

```

## Welfare

```{r, echo=F, fig.width=12, warning=F}
WELFARE_PLOT <-
  ggplot(WELFARE, aes(x = name, y = value)) +
  geom_boxplot(outlier.shape = 1,
               width = .25,
               fill = "gray") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Welfare change (%)",
       title = "% Change in welfare by counterfactual") +
  theme_hc()
outlier_annotations <- Outliers(WELFARE, WELFARE_PLOT)

(
  WELFARE_PLOT <-
    WELFARE_PLOT +
    geom_text_repel(
      data = outlier_annotations,
      aes(x = name, y = value, label = country),
      box.padding = 0.35,
      point.padding = 0.5,
      min.segment.length = unit(0, 'lines'),
      size = 3
    )
)


WELFARE_REGION_PLOT <-
  ggplot(WELFARE, aes(
    x = interaction(group, name),
    y = value,
    fill = group
  )) +
  geom_boxplot(outlier.shape = 1, width = .5) +
  facet_wrap(~ name, scales = "free_x", nrow = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start = .3, end = 1) +
  labs(x = "",
       y = "Welfare change (%)",
       title = "% Change in welfare by counterfactual",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(WELFARE, WELFARE_REGION_PLOT)


(
  WELFARE_REGION_PLOT <-
    WELFARE_REGION_PLOT +
    geom_text_repel(
      data = outlier_annotations,
      aes(
        x = interaction(group,name),
        y = value,
        label = country
      ),
      box.padding = 0.35,
      point.padding = 0.5,
      min.segment.length = unit(0, 'lines'),
      size = 3
    ) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part2)))
)
```

```{r, echo=FALSE, fig.width=12, warning=F}
ggplot(WELFARE[WELFARE$name == "No Response", ], aes(x = reorder(code, value), y = value)) +
  geom_bar(stat = "identity", fill="darkgray") +
  geom_point(data = WELFARE[WELFARE$name != "No Response", ],
             aes(x = code, y = value, shape = name), size = 2) +
  labs(x = "", y = "Welfare change %", shape = "", title = "% Change in welfare by counterfactual and country") + 
  theme(axis.text.x = element_text(angle = 25)) + 
  theme_hc()


WELFARE_SCATTER <- pivot_wider(WELFARE[WELFARE$name != "No Response", ])

ggplot(WELFARE_SCATTER) +
  geom_text(aes(x=`Response w/ equivalence`, y = `Response w/o equivalence`, label = code, color = group), size = 2) +
  labs(color = "", title = "% Change in Welfare: w/o equivalence vs w/ equivalence") +
  geom_abline(intercept = 0, slope = 1) +
  geom_hline(yintercept = 0, color = "gray") +
  geom_vline(xintercept = 0, color = "gray") +
  theme_hc()
```

## Trade flows

```{r, echo=FALSE, fig.width=10, fig.height=10, warning=F}
TRADE_FLOWS_PLOT <-
ggplot(TRADE_FLOWS, aes(x = interaction(trade_flow,name), y = value, fill = trade_flow)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, nrow = 1, scale = "free_x") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Multilateral changes in trade (%)",
       title = "% Change in multilateral trade flows by counterfactual",
       fill = "Trade flows") +
  theme_hc()

outlier_annotations <- Outliers(TRADE_FLOWS, TRADE_FLOWS_PLOT)

(TRADE_FLOWS_PLOT <-
  TRADE_FLOWS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(trade_flow, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3)) +
  scale_x_discrete(labels = rep(c("Exports", "Imports", length(CTF_part2))))


(TRADE_FLOWS_COALITION_PLOT <-
ggplot(TRADE_FLOWS_COALITION, aes(x = name, y = value, fill = trade_flow)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~interaction(coalition, name), scale = "free_x", ncol = 2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Multilateral changes in trade (%)",
       title = "% Change in multilateral trade flows within and outside of coalition",
       fill = "") +
  scale_x_discrete(labels = c(""))+
  theme_hc())



```

```{r, echo = F, fig.width=12, warning=F}
EXPORTS_PLOT <-
ggplot(EXPORTS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, nrow = 1, scale = "free_x") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Changes in exports (%)",
       title = "% Change in exports by counterfactual and region",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(EXPORTS, EXPORTS_PLOT)

(EXPORTS_PLOT<-
  EXPORTS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part2))))


IMPORTS_PLOT <-
ggplot(IMPORTS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, nrow = 1, scale = "free_x") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_fill_grey(start=.3, end=1) +
  labs(x = "",
       y = "Changes in imports (%)",
       title = "% Change in imports by counterfactual and region",
       fill = "Region") +
  theme_hc()
outlier_annotations <- Outliers(IMPORTS, IMPORTS_PLOT)

(IMPORTS_PLOT<-
  IMPORTS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part2))))

```

## Emissions 

```{r, echo = F, fig.width=12}
EMISSIONS_PLOT <-
ggplot(EMISSIONS, aes(x = name, y = value)) +
  geom_boxplot(fill = "gray", width = 0.5, outlier.shape = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Change in GHG emissions (%)",
       title = "% Change in GHG emissions by counterfactual") +
  theme_hc()

outlier_annotations <- Outliers(EMISSIONS, EMISSIONS_PLOT)

(EMISSIONS_PLOT<-
  EMISSIONS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = name, y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3))

EMISSIONS_REGIONS_PLOT <-
ggplot(EMISSIONS, aes(x = interaction(group, name), y = value, fill = group)) +
  geom_boxplot(outlier.shape = 1, width=.5) +
  facet_wrap(~name, nrow = 1, scale = "free_x") +
  scale_fill_grey(start=.3, end=1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "",
       y = "Changes in GHG emissions (%)",
       title = "% Change in GHG emissions by counterfactual and region",
       fill = "Region") +
  theme_hc()

outlier_annotations <- Outliers(EMISSIONS, EMISSIONS_REGIONS_PLOT)

(EMISSIONS_REGIONS_PLOT<-
  EMISSIONS_REGIONS_PLOT +
    geom_text_repel(data = outlier_annotations,
                    aes(x = interaction(group, name), y = value, label = country),
                    box.padding = 0.35, point.padding = 0.5,
                    min.segment.length = unit(0, 'lines'),
                    size = 3) +
    scale_x_discrete(labels = rep(c("Africa", "Eurasia", "LAC"), length(CTF_part2))))


```



